Deep mutational scanning of hemagglutinin helps predict evolutionary fates of human H3N2 influenza variants

### 2018-04-09 paper/cover_letter.tex
updates to cover letter

@@

We suggest the following potential reviewers.
We have included reviewers with expertise that spans the range of fields covered by our study:
\begin{itemize}
\item Michael Lassig (Cologne, \href{mailto:lassig@thp.uni-koeln.de}{lassig@thp.uni-koeln.de}) is a leading expert in predictive models of influenza virus evolution.
\item Joshua Plotkin (Penn, \href{mailto:jplotkin@sas.upenn.edu}{jplotkin@sas.upenn.edu}) is an expert on quantitative studies of virus evolution.
\item Nicholas Heaton (Duke, \href{mailto:nicholas.heaton@dm.duke.edu}{nicholas.heaton@dm.duke.edu}) is an expert on influenza virus.
\item Katia Koelle (Emory, \href{mailto:katia.koelle@emory.edu}{katia.koelle@emory.edu}) is an expert on influenza virus evolution.
\item Ren Sun (UCLA, \href{mailto:rsun@mednet.ucla.edu}{rsun@mednet.ucla.edu}) is an expert on the deep mutational scanning of virus proteins.
\item Colin Russell (AMC Amsterdam, \href{mailto:c.a.russell@amc.uva.nl}{c.a.russell@amc.uva.nl}) is an expert on influenza virus evolution.
\end{itemize}

>>>>

\pagestyle{empty}

@@

We suggest the following potential reviewers.
We have included reviewers with expertise that spans the range of fields covered by our study:
\begin{itemize}
\item Michael Lassig (Cologne, \href{mailto:lassig@thp.uni-koeln.de}{lassig@thp.uni-koeln.de}) is a leading expert in predictive models of influenza virus evolution.
\item Marta Luksza (Institute for Advanced Study, \href{mailto:mluksza@ias.edu}{mluksza@ias.edu}) is a leading expert in predictive models of influenza virus evolution.
\item Joshua Plotkin (Penn, \href{mailto:jplotkin@sas.upenn.edu}{jplotkin@sas.upenn.edu}) is an expert on quantitative studies of virus evolution.
\item Nicholas Heaton (Duke, \href{mailto:nicholas.heaton@dm.duke.edu}{nicholas.heaton@dm.duke.edu}) is an expert on influenza virus.
\item Sergey Kryazhimskiy (UCSD, \href{mailto:skryazhi@ucsd.edu}{mailto:skryazhi@ucsd.edu}) is an expert on quantitative studies of viral evolution.
\item Katia Koelle (Emory, \href{mailto:katia.koelle@emory.edu}{katia.koelle@emory.edu}) is an expert on influenza virus evolution.
\item Ren Sun (UCLA, \href{mailto:rsun@mednet.ucla.edu}{rsun@mednet.ucla.edu}) is an expert on viral deep mutational scanning.
\item Colin Russell (AMC Amsterdam, \href{mailto:c.a.russell@amc.uva.nl}{c.a.russell@amc.uva.nl}) is an expert on influenza virus.
\end{itemize}
